---
title: "HW1"
author: "Anya Kuznetsova"
date: "10/2/2021"
output: html_document
---

<style type="text/css">
  body{
  font-size: 12pt;
}
</style>

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(tibble)
library(dplyr)
library(ggplot2)
library(ggrepel)
library(ggridges)
library(ggbeeswarm)
```

## Visualization in R

The following plots are based on the data from this [file](https://raw.githubusercontent.com/dashapopova/Intro-to-R/main/HWs/heroes_information.csv).

```{r}
heroes <- read.csv("https://raw.githubusercontent.com/dashapopova/Intro-to-R/main/HWs/heroes_information.csv")
```

First of all we will exclude incorrectly specified data -- at least in cases where it is obvious:

```{r}
heroes <- heroes[heroes[, 7] != "-99", ]
heroes <- heroes[heroes[, 11] != "-99", ]
```

Now let's only count the two biggest publishers there are -- Marvel and DC -- since the others are insignificant comparing to these two:

```{r}
publishers_top2 = heroes[apply(heroes,1,function(x) {any(c("Marvel Comics", "DC Comics") %in% x)}),]
```

In our first plot we will take a look at the gender dependence of the height of human characters (for clarity). For simplicity, we will consider only those characters whose gender is indicated:

```{r}
h_publishers_top2 = publishers_top2[apply(publishers_top2,1,function(x) {any(c("Human") %in% x)}),]

fm_publishers_top2 = h_publishers_top2[apply(h_publishers_top2,1,function(x) {any(c("Female", "Male") %in% x)}),]
```

Here is our first plot:

```{r}
fm_publishers_top2 %>% 
  ggplot(aes(Gender, Height))+
  geom_violin(width = 0.3)+
  labs(x = "Gender of the hero",
  y = "Height of the hero",
  title = "Dependence of the human heroes height on their gender")
```

For our next plot let's consider not only human heroes but mutants too but now we will exclude 6 certain characters because their weight (the key parameter this time) is too big and will ruin our plot:

```{r}
hm_publishers_top2 = publishers_top2[apply(publishers_top2,1,function(x) {any(c("Mutant", "Human") %in% x)}),]

h_m_publishers_top2 <- hm_publishers_top2[!(hm_publishers_top2$name=="Juggernaut" | hm_publishers_top2$name=="Bloodaxe" | hm_publishers_top2$name=="A-Bomb" | hm_publishers_top2$name=="Onslaught" | hm_publishers_top2$name=="She-Hulk" | hm_publishers_top2$name=="Scorpion"),]
```

Here is our second plot:

```{r, fig.width=10,fig.height=6}
h_m_publishers_top2 %>% 
  ggplot(aes(Weight, Race, fill = Race)) +
  geom_rug()+
  geom_density_ridges(alpha = 0.57)+
  theme_bw()+
  labs(x = "Weight of hero",
       title = "Dependence of the heroes weight on their race (human and mutant)")
```

Now we will consider dependence of heroes height on their race.

Again we have to exclude singled out heroes of a very big height for them no too ruin the plot:

```{r}
noGiants_publishers_top2 <- publishers_top2[!(publishers_top2$Race=="-" | publishers_top2$name=="Fin Fang Foom" | publishers_top2$name=="Galactus" | publishers_top2$name=="Groot"),]
```

Here is a histogram of all races:

```{r, fig.width=10,fig.height=6}
noGiants_publishers_top2 %>% 
  ggplot(aes(Height, fill = Race)) +
  geom_rug()+
  geom_histogram() +
  theme_bw()+
  labs(x = "Height of hero",
       title = "Dependence of the heroes height on their race")
```

Now let's concentrate on humans and mutants again (because these two races have the biggest number of heroes):

```{r, fig.width=5.5,fig.height=8}
hm_noGiants_publishers_top2 = noGiants_publishers_top2[apply(noGiants_publishers_top2,1,function(x) {any(c("Mutant", "Human") %in% x)}),]

ggplot(data = hm_noGiants_publishers_top2, aes(Height, fill = Race)) +
  geom_dotplot(method = "histodot") +
  scale_y_continuous(NULL, breaks = NULL) +
  theme_bw()+
  labs(x = "Height of hero",
       title = "Dependence of the heroes height on their race (human and mutant)")
```

And in our final plot we will study dependence of the heroes size on their skin color -- just for fun, i guess.

Once again we are removing all "giants" and all heroes whose skin color isn't specified:

```{r}
normal_publishers_top2 <-  publishers_top2[!(publishers_top2$name=="Fin Fang Foom" | publishers_top2$name=="Galactus" | publishers_top2$name=="Groot" | publishers_top2$name=="Juggernaut" | publishers_top2$name=="Bloodaxe" | publishers_top2$name=="A-Bomb" | publishers_top2$name=="Onslaught" | publishers_top2$name=="She-Hulk" | publishers_top2$name=="Scorpion" | publishers_top2$Skin.color=="-"),]
```

Colors of dots represent color of heroes skin. Although this plot is not very representative because in this dataset the skin color is indicated only for a small number of heroes.

```{r, fig.width=10,fig.height=7}
normal_publishers_top2 %>%
  ggplot(aes(Height, Weight, color = Skin.color))+
  geom_point() + 
  labs(x = "Height of the hero",
       y = "Weight of the Hero",
       title = "Dependence of the heroes size on their skin color") +
  theme(legend.position = "bottom") +
  scale_color_manual(values = c("blue", "#ADD8E6", "gold", "green", "#231F20", "orange", "pink", "purple", "red", "#C0C0C0", "white", "yellow"))

```